---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# r6qualitytools

<!-- badges: start -->

<!-- [![CRAN status](https://www.r-pkg.org/badges/version/r6qualitytools)](https://CRAN.R-project.org/package=r6qualitytools) -->
[![Codecov test coverage](https://codecov.io/gh/Fabianenc/r6qualitytools/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Fabianenc/r6qualitytools?branch=main) [![R-CMD-check](https://github.com/Fabianenc/r6qualitytools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Fabianenc/r6qualitytools/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/r6qualitytools)](https://CRAN.R-project.org/package=r6qualitytools)
<!-- badges: end -->

The goal of **r6qualitytools** is to provide a comprehensive suite of statistical tools for Quality Management, designed around the Define, Measure, Analyze, Improve, and Control (DMAIC) cycle used in Six Sigma methodology. It builds on the original discontinued CRAN package **qualitytools**, enhancing it with R6 object-oriented programming, modernizing the graphics with **ggplot2** and **plotly**, and adopting **tidyverse** principles for data manipulation and visualization.

## Installation

```{r, eval = FALSE}
install.packages("r6qualitytools")
library("r6qualitytools")
```

## Overview

**r6qualitytools** includes various tools to manage quality science processes efficiently:

-   **DMAIC methodology**: tools designed around the Six Sigma cycle.
-   **R6-based design**: uses R6 classes for flexibility and performance.
-   **Interactive graphics**: modern visualizations with **ggplot2** and **plotly**.
-   **tidyverse integration**: easy data manipulation and visualization.

It supports a variety of analyses relevant to quality management, offering an intuitive interface for both beginners and advanced users.

For more details, see the package documentation.

## Usage

You can use the package to generate statistical models and control charts efficiently. Here are basic examples that demonstrates the use of the package:

```{r}
library(r6qualitytools)

# Object of Class Distr - Normal
set.seed(123)
data <- rnorm(100, mean = 5, sd = 2)
parameters <- list(mean = 5, sd = 2)
distr <- Distr$new(x = data, name = "normal", parameters = parameters, sd = 2, n = 100, loglik = -120)
distr$plot()
```

```{r}
# Class DistrCollection
data2 <- rpois(100, lambda = 3)
parameters2 <- list(lambda = 3)
distr2 <- Distr$new(x = data2, name = "poisson", parameters = parameters2, sd = sqrt(3), n = 100, loglik = -150)
distr2$plot()

collection <- DistrCollection$new()
collection$add(distr)
collection$add(distr2)
collection$summary()
```

```{r}
# qqPlot and ppPlot
set.seed(1234)
x <- rnorm(20, mean = 20)
qqPlot(x, "normal", bounds.lty = 3, bounds.col = "red")
ppPlot(x, "normal", bounds.lty = 3, bounds.col = "red")
```

```{r, message=FALSE, warning=FALSE}
# Gage capacity
x <- c( 9.991, 10.013, 10.001, 10.007, 10.010, 10.013, 10.008, 10.017, 10.005, 10.005, 10.002,
        10.017, 10.005, 10.002, 9.996, 10.011, 10.009 , 10.006, 10.008, 10.003, 10.002, 10.006, 
        10.010, 9.992, 10.013)

cg(x, target = 10.003, tolerance = c(9.903, 10.103))
```

```{r}
# Process Capability
set.seed(1234)
data <- rnorm(20, mean = 20)
pcr(data, "normal", lsl = 17, usl = 23)
```

```{r}
# Gage R&R Design
gdo <- gageRRDesign(Operators = 3, Parts = 10, Measurements = 3, randomize = FALSE, method='nested')
# vector of responses
y <- c(0.29,0.08, 0.04,-0.56,-0.47,-1.38,1.34,1.19,0.88,0.47,0.01,0.14,-0.80,
      -0.56,-1.46, 0.02,-0.20,-0.29,0.59,0.47,0.02,-0.31,-0.63,-0.46,2.26,
      1.80,1.77,-1.36,-1.68,-1.49,0.41,0.25,-0.11,-0.68,-1.22,-1.13,1.17,0.94,
      1.09,0.50,1.03,0.20,-0.92,-1.20,-1.07,-0.11, 0.22,-0.67,0.75,0.55,0.01,
      -0.20, 0.08,-0.56,1.99,2.12,1.45,-1.25,-1.62,-1.77,0.64,0.07,-0.15,-0.58,
      -0.68,-0.96,1.27,1.34,0.67,0.64,0.20,0.11,-0.84,-1.28,-1.45,-0.21,0.06,
      -0.49,0.66,0.83,0.21,-0.17,-0.34,-0.49,2.01,2.19,1.87,-1.31,-1.50,-2.16)
gdo$response(y)

gdo <- gageRR(gdo, method='nested')

# Using Plots
gdo$errorPlot()
gdo$whiskersPlot()
gdo$averagePlot()
gdo$compPlot()
```

```{r}
# Factorial Designs
vp.full <- facDesign(k = 3)
y = rnorm(2^3)
vp.full$.response(y)
vp.full$summary()
vp.full$effectPlot()

# Plots
paretoPlot(vp.full, p.col = "Pastel1")
normalPlot(vp.full)
contour1 <- contourPlot(A,B,y, data = vp.full)
contour1$plot
```

```{r}
# Mix Design
mdo <- mixDesign(3, 2, center = FALSE, axial = FALSE, randomize = FALSE, replicates = c(1, 1, 2, 3))

mdo$names(c("polyethylene", "polystyrene", "polypropylene"))
elongation <- c(11.0, 12.4, 15.0, 14.8, 16.1, 17.7, 16.4, 16.6, 8.8, 10.0, 10.0, 9.7, 11.8, 16.8, 16.0)
mdo$.response(elongation)
mdo$summary()

contour3 <- contourPlot3(A, B, C, elongation, data = mdo, form = "quadratic")
contour3$plot

```

```{r}
# Taguchi Design
tdo <- taguchiDesign("L9_3",randomize=F)
tdo$values(list(A = c("material 1", "material 2", "material 3"), B = c(29, 30, 35)))
tdo$names(c("Factor 1", "Factor 2", "Factor 3", "Factor 4"))
set.seed(1)
tdo$.response(rnorm(9))
tdo$summary()
tdo$effectPlot()
```

```{r}
# Plackett-Burman Design
pbdo<- pbDesign(26)
pbdo$summary()
```

```{r}
# gageLin Design
A=c(2.7,2.5,2.4,2.5,2.7,2.3,2.5,2.5,2.4,2.4,2.6,2.4)
B=c(5.1,3.9,4.2,5,3.8,3.9,3.9,3.9,3.9,4,4.1,3.8)
C=c(5.8,5.7,5.9,5.9,6,6.1,6,6.1,6.4,6.3,6,6.1)
D=c(7.6,7.7,7.8,7.7,7.8,7.8,7.8,7.7,7.8,7.5,7.6,7.7)
E=c(9.1,9.3,9.5,9.3,9.4,9.5,9.5,9.5,9.6,9.2,9.3,9.4)

test=gageLinDesign(ref=c(2,4,6,8,10),n=12)
Messungen=data.frame(rbind(A,B,C,D,E))
test$response(Messungen)
test$summary()

MSALin=gageLin(test,lty=c(3,4), plot = FALSE)
MSALin$plot()
```

## Getting help

If you encounter any issues or have questions, please file an issue with a reproducible example at the [GitHub repo](https://github.com/Fabianenc/r6qualitytools/issues).
